Emulsions Stabilized by Magnetic Ellipsoidal Particles: A Lattice Boltzmann Study

### 2025-04-15 chapters/LBM_technique.tex
resolved some other notation issues

where $\vec{f}$ is the force exerted on the fluid from external forces such as gravity or magnetic interactions and $\vec{\vec{\sigma}}$ is the stress tensor. 
For a Newtonian, isotropic fluid, the viscous stress tensor is given by

\begin{equation}
    \vec{\vec{\sigma}} = -P\mathbb{I} + \eta\left( \nabla \vec{u} + (\nabla \vec{u})^T\right) - \frac{2}{3}(\nabla \cdot \vec{u})\mathbb{I} 
\end{equation}

@@

\begin{equation}
    \begin{split}
    \vec{F_p} = m_p \frac{\vec{u}_p}{dt} , \\
    \vec{D_p} = \vec{J}_p \frac{\vec{\omega}_p}{dt} ,
    \label{eq:md}
    \end{split}
\end{equation}

@@

\begin{equation}
    \vec{F}_{ij} = \frac{3 \mu_0 m_i m_j}{4 \pi} [\frac{5( \Hat{\vec{o_i}} \cdot \Hat{\vec{r_{ij}}} )(\Hat{\vec{o_j}}
    \cdot \Hat{\vec{r_{ij}}})}{|\vec{r_{ij}}^4|}\Hat{\vec{r_{ij}}} - \frac{(\Hat{\vec{o_i}} \cdot \Hat{\vec{o_j}})\Hat{\vec{r_{ij}}} + 
    (\Hat{\vec{o_i}} \cdot \Hat{\vec{r_{ij}}})\Hat{\vec{o_j}} + (\Hat{\vec{o_j}} \cdot \Hat{\vec{r_{ij}}})\Hat{\vec{o_j}} }{|\vec{r_{ij}}|^4}]
\label{eq:dipole_magnetic_force}
\end{equation}

\begin{equation}
    \vec{T}_{ij} = \frac{\mu_0 m_i m_j}{4 \pi}[ \frac{3(\Hat{\vec{o_j}} \cdot \Hat{\vec{r_{ij}}})\Hat{\vec{o_i}} \times \Hat{\vec{r_{ij}}} }
    {|\vec{r}_{ij}|^3} - \frac{\Hat{\vec{o_i}} \cdot \Hat{\vec{o_j}} }{|\vec{r}_{ij}|^3} ]
    \label{eq:dipole_magnetic_torque}
\end{equation}

>>>>

where $\vec{f}$ is the force exerted on the fluid from external forces such as gravity and $\vec{\vec{\sigma}}$ is the stress tensor. 
For a Newtonian, isotropic fluid, the stress tensor is given by

\begin{equation}
    \vec{\vec{\sigma}} = -P\mathbb{I} + \eta\left( \nabla \vec{u} + (\nabla \vec{u})^T - \frac{2}{3}(\nabla \cdot \vec{u})\mathbb{I} \right)
\end{equation}

@@

\begin{equation}
    \begin{split}
    \vec{F_p} = m_p \frac{d \vec{u}_p}{dt} , \\
    \vec{D_p} = \vec{J}_p \frac{d \vec{\omega}_p}{dt} ,
    \label{eq:md}
    \end{split}
\end{equation}

@@

\begin{equation}
    \vec{F}_{ij} = \frac{3 \mu_0 m_i m_j}{4 \pi} \left[ \frac{5( \Hat{\vec{o_i}} \cdot \Hat{\vec{r_{ij}}} )(\Hat{\vec{o_j}}
    \cdot \Hat{\vec{r_{ij}}})}{|\vec{r_{ij}}^4|}\Hat{\vec{r_{ij}}} - \frac{(\Hat{\vec{o_i}} \cdot \Hat{\vec{o_j}})\Hat{\vec{r_{ij}}} + 
    (\Hat{\vec{o_i}} \cdot \Hat{\vec{r_{ij}}})\Hat{\vec{o_j}} + (\Hat{\vec{o_j}} \cdot \Hat{\vec{r_{ij}}})\Hat{\vec{o_j}} }{|\vec{r_{ij}}|^4} \right]
\label{eq:dipole_magnetic_force}
\end{equation}

\begin{equation}
    \vec{T}_{ij} = \frac{\mu_0 m_i m_j}{4 \pi}\left[ \frac{3(\Hat{\vec{o_j}} \cdot \Hat{\vec{r_{ij}}})\Hat{\vec{o_i}} \times \Hat{\vec{r_{ij}}} }
    {|\vec{r}_{ij}|^3} - \frac{\Hat{\vec{o_i}} \cdot \Hat{\vec{o_j}} }{|\vec{r}_{ij}|^3}\right]
    \label{eq:dipole_magnetic_torque}
\end{equation}
